---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MLR)
```

# Example 1: Simple Linear Regression

## Fit linear model on dataset

To fit a linear model, simply input a formula and dataset to the `regression_fit()` fit function. This produces a list containing the following objects:

* `formula`: the model formula
* `dimensions`: the number of observations and covariates
* `residuals`: the model residuals, as a vector
* `fitted_values`: the fitted values of the model, as a vector
* `coefficients`: the estimated coefficients, as a table, which also contains the results of a two-sided t-test
* `variance_covariance`: the variance-covariance matrix, and
* `r_squared`: the R-squared and adjusted R-square, as a vector of length 2
```{r fit}
data(iris)
form <- Sepal.Length ~ Sepal.Width

model1 <- regression_fit(formula = form, data = iris)
print(model1$coefficients)
```

## Compare results to base functions

Below, we test to ensure that our results align with the standard output from base R alternatives. One advantage of `regression_fit()`, you might observe, is that one can access important model components without needing to use additional functions like `summary()` or `vcov()`.

```{r test}
model2 <- lm(formula = form, data = iris)
model2_sum <- summary(model2)

#Check coefficients
all.equal(model1$coefficients, model2_sum$coefficients)

#Check confidence intervals
all.equal(model1$confidence_intervals,confint(model2))

#Check residuals
all.equal(model1$residuals, model2$residuals, check.attributes = F)

#Check fitted values
all.equal(model1$fitted_values, model2$fitted.values, check.attributes = F)

#Check variance-covariance
all.equal(model1$variances, vcov(model2), check.attributes = F)

#Check F test
all.equal(model1$anova$f_value, model2_sum$fstatistic["value"], check.attributes = F)

#Check R-squared
model2_rsq <- c(model2_sum$r.squared, model2_sum$adj.r.squared)
all.equal(model1$r_squared, model2_rsq, check.attributes = F)
```


## Compare speed to base functions
Next, we compare the efficiency of `regression_fit()` to `lm()` using the `bench` package. We can see in the output table below that the `lm()` function is marginally faster on average.

```{r compare, message=FALSE}
library(bench)

bench::mark(
  regression_fit(form, iris)$coefficients,
  summary(lm(form, iris))$coefficients
)

```

# Example 2: Multiple Linear Regression

## Fit linear model on dataset

We can fit a multiple regression model in the same way as an SLR. Here, we have also specified a particular `alpha` to use in our confidence intervals, instead of using the default of 0.05. 
```{r fit2}
form2 <- Sepal.Length ~ Sepal.Width + Petal.Length + Species

model1 <- regression_fit(formula = form2, data = iris, alpha = 0.1)
print(model1$coefficients)
```

## Compare results to base functions

Once again, we test the results below. All match the output provided by base R functions.

```{r test2}
model2 <- lm(formula = form2, 
             data = iris)

model2_sum <- summary(model2)

#Check coefficients
all.equal(model1$coefficients, model2_sum$coefficients)

#Check confidence intervals
all.equal(model1$confidence_intervals,confint(model2, level = 0.9))

#Check residuals
all.equal(model1$residuals, model2$residuals, check.attributes = F)

#Check fitted values
all.equal(model1$fitted_values, model2$fitted.values, check.attributes = F)

#Check variance-covariance
all.equal(model1$variances, vcov(model2), check.attributes = F)

#Check F test
all.equal(model1$anova$f_value, model2_sum$fstatistic["value"], check.attributes = F)

#Check R-squared
model2_rsq <- c(model2_sum$r.squared, model2_sum$adj.r.squared)
all.equal(model1$r_squared, model2_rsq, check.attributes = F)
```


## Compare speed to base functions
Lastly, we compare the speed of `regression_fit()` and `lm()` for multiple linear regression. Like before, we find that the base R function might be marginally faster, but the results do vary slightly from one trial to the next.

```{r compare2, message=FALSE}
bench::mark(
  regression_fit(form2, iris)$coefficients,
  summary(lm(form2, iris))$coefficients
)
```
